Should I Airbnb My Property?

### 2017-03-06 abb_Writeup.Rmd
logit model tables and chunk cleanup

---
title: "Should I Airbnb My Property?"
author: "Andy Krause and Gideon Aschwanden"
header-includes:
    - \usepackage{setspace}\doublespacing
date: "February 17, 2017"
output:
  pdf_document: default
  html_document: default
geometry: margin=3.3cm
bibliography: abb.bib
---

@@

   load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
a <- 1

@@

```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
  data.path <- 'c:/dropbox/research/airBNB/data/'
  load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))
```

```{r load_ptplot, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}

@@

@@

```{r ltype_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals'}

@@

```{r bb_comp, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Bed/Baths by Property Type'}

@@

```{r ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents'}

@@

```{r locmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets'}

@@

```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE}

@@

```{r loc.plots, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps'}

@@

```{r loc.bars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Submarket Observation Counts'}

@@

```{r, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary'}

@@

```{r revdensity.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions'}

@@

As the difference between extrapolated and potential revenue suggests, many short-term hosts are not listing their properties full-time.  There may be, therefore, different types of hosts operating in the Airbnb market. from anecdotal evidence, there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property when very infrequently, for example when they are away on vacation (Opportunistic Sharers).
If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked shoudl be very bi-modal with profit seekers on the left and opportunistic sharers on the right. The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.  
There is also a third potential host type, that of the host who utilizies multiple platforms, of which Airbnb may just be one, to list their short-term property. A potential method to identify these hosts is to look at the number of individual periods of blocked days.  A host using multiple platforms will likely have many, small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms. We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 9. We do find many host with a large number of blocked periods, but, unfortunately, no true pattern emerges.

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

@@

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5}

@@

@@

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

@@

str.data$host.type <- 'Unknown'
str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
str.data$host.type <- factor(str.data$host.type,
                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                      'Multi-Platform User', 'Unknown'))

@@

@@

@@

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}

@@

host.type.bar
```

@@

<!-- The analyses above show that, overall, just less than 1 out of every 3 Airbnb'd properties was actually  more profitable as a short-term rental then it would have been if rented long-term over the course of the year.  This proportion, however, varied by location and property type.  While illustrative, the above do not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.  To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below. -->

<!-- We specify three, increasingly complex, logistic regression models.  Model 1 takes the form of: -->

<!-- \begin{equation} -->
<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon -->
<!-- \end{equation} -->

<!-- where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term prefernce, $PType$ is the property type (apt or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term. -->

<!-- For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.  -->

<!-- \begin{equation} -->
<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon -->
<!-- \end{equation} -->

<!-- Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts: -->

<!-- \begin{equation} -->
<!-- ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + -->
<!-- \beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon -->
<!-- \end{equation} -->

<!-- where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.  We have normalized this by bedroom to avoid co-linearity in our model with the bedroom variables.], $MinStay$ is the minimum number of nights that a stay may have and $CancelPolicy$ is the difficulty with which a booking may be cancelled.  We have grouped the cancellation policies into three groups, Flexible (24 hour notice), Moderate (5 day notice) and Strict (50\% refund, 7, 30 or 60 day notice required). -->

<!-- The results of all three models are shown in Table 7. For $PType$ apartments are the reference category,  for $BedBath$, 2Bed/2Bath is the reference category, for $Submrkt$ the Core is the reference category and for $CancelPolicy$ moderate is the reference category.  As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.   -->

<!-- In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in the short-term than apartments.  Small 1Bed/1Bath properties have a lower probability of being preferable in the short term than the reference class (2Bed/2Bath), while larger 3Bed/2Bath and 4Bed/2Bath have much higher probability of short term preference. -->

<!-- Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the core (the reference category) when controlling for structural characteristics.  These findings mirror those found above in Table 9.  The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.   -->

<!-- Finally, in Model 3 we add in host behavior or policies. Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.  This variable may be operating a proxy for additional sleeping spaces which allow for a higher nightly rate, ceteris paribus, to be charged.  The greater the minimum stay, the lower the probability of short-term preference.  Longer minimum stay may equate to lower occupancy rates as one or two night travelers are exempted from the property.  Owners with longer minimum stays may be looking to minimize costs such as cleaning and administration.  Flexible cancellation policies result in a lower probability of short-term preference, while a Strict policy has a weak, but positive relationship with short-term preference.  Strict policies do help maintain revenues, but may also scare off some potential guests.  Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand.   -->

<!-- ```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'} -->

<!--  names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3") -->
<!--  x.full <- xtable(full.table, -->
<!--                   caption='Logistic Modeling Results\n') -->
<!--  align(x.full) <- 'lllll' -->

<!--  print(x.full,  -->
<!--        include.rownames=FALSE,  -->
<!--        hline.after=c(-1,0,15,20,20),  -->
<!--        caption.placement='top') -->

<!-- ``` -->

<!-- \pagebreak -->

>>>>

---
title: "Should I Airbnb My Property?"
author: "Andy Krause and Gideon Aschwanden"
date: "February 17, 2017"
output:
  pdf_document: default
  html_document: default
header-includes: \usepackage{setspace}\doublespacing
geometry: margin=3.3cm
bibliography: abb.bib
---

@@

   load(paste0(data.path, '/analyzed/analyzed_workspace.RData'))

@@

&nbsp;

```{r plot_pt, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide', fig.height=3, fig.cap='Tenure Type by Property Type', fig.lp='typecomp'}

@@

&nbsp;

@@

&nbsp;

```{r plot_ltype, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=2.5, fig.width=3.75, fig.cap='Listing Type of Short Term Rentals', fig.lp='ltcomp'}

@@

&nbsp;

```{r plot_bb, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=5.75, fig.cap='Bed/Baths by Property Type', fig.lp='bbcomp'}

@@

&nbsp;

```{r plot_ratesrents, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3, fig.width=5.75, fig.cap='Distribution of Rates and Rents', fig.lp='rrcomp'}

@@

&nbsp;

```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.width=4, fig.cap='Melbourne Submarkets', fig.lp='submap'}

@@

&nbsp;

```{r table_corelist, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='List of Core Suburbs', fig.lp='coresuburbs'}

@@

&nbsp;

```{r plot_locations, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=5.5, fig.height=9, fig.cap='Location Maps', fig.lp='locmaps'}

@@

&nbsp;

```{r plot_locbars, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=8.5, fig.height=4, fig.cap='Submarket Observation Counts', fig.lp='locbars'}

@@

&nbsp;

```{r table_cleansummary, results="asis", comment=FALSE, message=FALSE, echo=FALSE, fig.cap='Data Cleaning Summary', fig.lp='cleansumm'}

@@

&nbsp;

```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5, fig.cap='Comparison of Revenue Distributions', fig.lp='revdens'}

@@

As the difference between extrapolated and potential revenue suggests, many short-term hosts are not listing their properties full-time.  There may be, therefore, different types of hosts operating in the Airbnb market. from anecdotal evidence, there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property when very infrequently, for example when they are away on vacation (Opportunistic Sharers).

If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked shoudl be very bi-modal with profit seekers on the left and opportunistic sharers on the right. The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.

There is also a third potential host type, that of the host who utilizies multiple platforms, of which Airbnb may just be one, to list their short-term property. A potential method to identify these hosts is to look at the number of individual periods of blocked days.  A host using multiple platforms will likely have many, small periods of blocked days on Airbnb as they will block out those days in which reservations are made on other platforms. We test to see if this is a meaningful metric by plotting the total count of blocked periods versus the percentage of blocked days in the right panel of Figure 9. We do find many host with a large number of blocked periods, but, unfortunately, no true pattern emerges.

&nbsp;

```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

@@

```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

@@

```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Blocking Tendencies', fig.lp='hostblock'}

@@

&nbsp;

```{r calc_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

@@

str.data$host.type <- 'Unknown'
str.data$host.type[str.data$blockpertime > 12] <- 'Multi-Platform User'
str.data$host.type[str.data$block.rate <= .25] <- 'Profit Seeker'
str.data$host.type[str.data$block.rate >= .75] <- 'Opportunistic Sharer'
str.data$host.type <- factor(str.data$host.type,
                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                      'Multi-Platform User', 'Unknown'))
```

```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

@@

```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

@@

```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5, fig.caption='Host Categories', fig.lp='hosttypes'}

@@

&nbsp;

```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4, fig.caption='Host Type Counts', fig.lp='hostbar'}

@@

host.type.bar

&nbsp;

@@

The analyses above show that, overall, just less than 1 out of every 3 Airbnb'd properties was actually more profitable as a short-term rental then it would have been if rented long-term over the course of the year. This proportion, however, varied by location and property type, with apartments and city-core properties showing the highest likelihood of short-erm preference. While illustrative, the above do not fully control for property characteristics or owner actions -- which are a key component of short-term rental success.  To better understand which factors are related to a higher likelihood of short-term preference, we develop a set of logistic regression models below.

We specify three, increasingly complex, logistic regression models.  Model 1 takes the form of:

\begin{equation}
ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \epsilon
\end{equation}

where $StPref$ is the probability of short-term preference, $\frac{STPref}{1-STPref}$ is the log-likelihood of short-term prefernce, $PType$ is the property type (apt or house), $BedBath$ is the bedroom and bathroom combination of the property and $\epsilon$ is an error term.

For Model 2 we add the five geographic submarkets, $SubMrkt$ to better control for geographic variation in the probabilities.

\begin{equation}
ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + \beta_{2} BedBath + \beta_{3} SubMrkt + \epsilon
\end{equation}

Finally, in Model 3 we add three variables describing policies set by the Airbnb hosts:

\begin{equation}
ln(\frac{STPref}{1-STPref}) = \beta_{0} + \beta_{1} PType + 
\beta_{2} BedBath + \beta_{3} SubMrkt +
\beta_3 GPR + \beta_{4} MinStay + \beta_5 CancelPolicy +  \epsilon
\end{equation}

where $GPR$ is the total number of guests allowed per bedroom^[Hosts set the total number of guests.  We have normalized this by bedroom to avoid co-linearity in our model with the bedroom variables.], $MinStay$ is the minimum number of nights that a stay may have and $CancelPolicy$ is the difficulty with which a booking may be cancelled.  We have grouped the cancellation policies into three groups, Flexible (24 hour notice), Moderate (5 day notice) and Strict (50\% refund, 7, 30 or 60 day notice required).

The results of all three models are shown in Table 7. For $PType$ apartments are the reference category,  for $BedBath$, 2Bed/2Bath is the reference category, for $Submrkt$ the Core is the reference category and for $CancelPolicy$ moderate is the reference category.  As the additional variables are added, the model fit diagnostics steadily increase, suggesting that the increased complexity of the models adds to the quality of the fit.

In Model 1, we see that when controlling for structural characteristics, Houses have a significantly lower probability of being more profitable in the short-term than apartments.  Small 1Bed/1Bath properties have a lower probability of being preferable in the short term than the reference class (2Bed/2Bath), while larger 3Bed/2Bath and 4Bed/2Bath have much higher probability of short term preference.

Adding the submarket variables (Model 2) shows that all areas have a much lower probability of short-term prefernce when compared to the core (the reference category) when controlling for structural characteristics.  These findings mirror those found above in Table 9.  The coefficients for the structural characteristics change little from Model 1 to Model 2, speaking the robustness of those estimates.

Finally, in Model 3 we add in host behavior or policies. Allowing a greater number of guests per bedroom results in a higher probability of short-term preference.  This variable may be operating a proxy for additional sleeping spaces which allow for a higher nightly rate, ceteris paribus, to be charged.  The greater the minimum stay, the lower the probability of short-term preference.  Longer minimum stay may equate to lower occupancy rates as one or two night travelers are exempted from the property.  Owners with longer minimum stays may be looking to minimize costs such as cleaning and administration.  Flexible cancellation policies result in a lower probability of short-term preference, while a Strict policy has a weak, but positive relationship with short-term preference.  Strict policies do help maintain revenues, but may also scare off some potential guests.  Strict cancellation may be a luxury for the best and highly desired properties on the market and, within our model, may be acting as a proxy for some unobserved measure of quality or demand.

&nbsp;

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference'}

 m1 <- as.data.frame(summary(pref.models[[1]])$coefficients)
 m2 <- as.data.frame(summary(pref.models[[2]])$coefficients)
 m3 <- as.data.frame(summary(pref.models[[3]])$coefficients)

 makeStatSig <- function(x){
   x <- as.numeric(x)
   y <- rep('***', length(x))
   y[x>.01] <- '** '
   y[x>.05] <- '*  '
   y[x>.1] <- '   '
   y
 }
 m1sig <- makeStatSig(m1[,4])
 m2sig <- makeStatSig(m2[,4])
 m3sig <- makeStatSig(m3[,4])

 m1$table.coef <- paste0(ifelse(m1$Estimate>0, ' ', ''), 
                         sprintf('%.3f', round(m1$Estimate,3)),
                         m1sig)
 m2$table.coef <- paste0(ifelse(m2$Estimate>0, ' ', ''),
                         sprintf('%.3f',round(m2$Estimate,3)),
                         m2sig)
 m3$table.coef <- paste0(ifelse(m3$Estimate>0, ' ', ''),
                         sprintf('%.3f',round(m3$Estimate,3)),
                         m3sig)

 m1c <- c(m1$table.coef, rep(' ', nrow(m3)-nrow(m1)))
 m2c <- c(m2$table.coef, rep(' ', nrow(m3)-nrow(m2)))
 m3c <- m3$table.coef

 full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
 names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '4 Bed & 2 Bath', 'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)', 
                          'Beach (Submarket)', 'Guests per Bedroom', 
                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')

 ## Create model diagnostics

  # Custom function
  logDx <- function(log.model, data, resp.var){

    pred <- prediction(predict(log.model, data, type='response'), resp.var)
    auc <- performance(pred, measure='auc')
    ll <- logLik(log.model)
    AIC <- AIC(log.model)

    return(list(AIC=AIC,
                logLik=ll,
                auc=auc))
  }

  # Extract diagnostics
  str.dx <- logDx(pref.models[[1]], str.data.ic, str.data.ic$str.ext.pref)
  sm.dx <- logDx(pref.models[[2]], str.data.ic, str.data.ic$str.ext.pref)
  host.dx <- logDx(pref.models[[3]], str.data.ic, str.data.ic$str.ext.pref)

  # Create diagnostic table
  diag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
                                      'AUC'),
                           Str.Model=c('', '', round(str.dx$AIC,0), 
                                       round(str.dx$logLik, 0),
                                       round(as.numeric(str.dx$auc@y.values),
                                             3)),
                           Sm.Model=c('', '', round(sm.dx$AIC,0), 
                                      round(sm.dx$logLik, 0),
                                      round(as.numeric(sm.dx$auc@y.values), 3)),
                           Host.Model=c('', '', round(host.dx$AIC,0), 
                                        round(host.dx$logLik, 0),
                                        round(as.numeric(host.dx$auc@y.values),
                                              3)))
  names(diag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")

 ## Combine into full table of coef and diags
  #full.table[,2] <- gsub(" ", "&nbsp;", full.table[,2], fixed=TRUE)

 full.table <- rbind(full.table, diag.table)

 x.full <- xtable(full.table,
                  caption='Logistic Modeling Results\n')
 align(x.full) <- 'lllll'

 print(x.full,
       include.rownames=FALSE,
       hline.after=c(-1,0,15,20,20),
       caption.placement='top')

&nbsp;

### Sensitivity Tests

#### Potential Revenue

Look at difference if using potential revenue

-- Show differences in global numbers and heat maps
-- Re-do the logistic models with potential revenue

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Logistic Model Results of Short Term Preference', fig.lp='xxx'}

 pm1 <- as.data.frame(summary(pref.models[[4]])$coefficients)
 pm2 <- as.data.frame(summary(pref.models[[5]])$coefficients)
 pm3 <- as.data.frame(summary(pref.models[[6]])$coefficients)

 pm1sig <- makeStatSig(pm1[,4])
 pm2sig <- makeStatSig(pm2[,4])
 pm3sig <- makeStatSig(pm3[,4])

 pm1$table.coef <- paste0(ifelse(pm1$Estimate>0, ' ', ''), 
                         sprintf('%.3f', round(pm1$Estimate,3)),
                         pm1sig)
 pm2$table.coef <- paste0(ifelse(pm2$Estimate>0, ' ', ''),
                         sprintf('%.3f',round(pm2$Estimate,3)),
                         pm2sig)
 pm3$table.coef <- paste0(ifelse(pm3$Estimate>0, ' ', ''),
                         sprintf('%.3f',round(pm3$Estimate,3)),
                         pm3sig)

 pm1c <- c(pm1$table.coef, rep(' ', nrow(pm3)-nrow(pm1)))
 pm2c <- c(pm2$table.coef, rep(' ', nrow(pm3)-nrow(pm2)))
 pm3c <- pm3$table.coef

 pfull.table <- as.data.frame(cbind(rep('x', length(pm1c)), pm1c, pm2c, pm3c))
 names(pfull.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 pfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '4 Bed & 2 Bath', 'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)', 
                          'Beach (Submarket)', 'Guests per Bedroom', 
                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')

 ## Create model diagnostics

  # Extract diagnostics
  pstr.dx <- logDx(pref.models[[4]], str.data.ic, str.data.ic$str.pot.pref)
  psm.dx <- logDx(pref.models[[5]], str.data.ic, str.data.ic$str.pot.pref)
  phost.dx <- logDx(pref.models[[6]], str.data.ic, str.data.ic$str.pot.pref)

  # Create diagnostic table
  pdiag.table <- data.frame(Variable=c('', 'Diagnostics', 'AIC', 'LogLik',
                                      'AUC'),
                           Str.Model=c('', '', round(pstr.dx$AIC,0), 
                                       round(pstr.dx$logLik, 0),
                                       round(as.numeric(pstr.dx$auc@y.values),
                                             3)),
                           Sm.Model=c('', '', round(psm.dx$AIC,0), 
                                      round(psm.dx$logLik, 0),
                                      round(as.numeric(psm.dx$auc@y.values),
                                            3)),
                           Host.Model=c('', '', round(phost.dx$AIC,0), 
                                        round(phost.dx$logLik, 0),
                                        round(as.numeric(phost.dx$auc@y.values),
                                              3)))
  names(pdiag.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")

 ## Combine into full table of coef and diags
  #full.table[,2] <- gsub(" ", "&nbsp;", full.table[,2], fixed=TRUE)

 pfull.table <- rbind(pfull.table, pdiag.table)

 px.full <- xtable(pfull.table,
                   caption='Logistic Modeling Results\n')
 align(px.full) <- 'lllll'

 print(px.full,
       include.rownames=FALSE,
       hline.after=c(-1, 0, 15, 20, 20),
       caption.placement='top')

#### Host Classification

Look at difference if breaking down by host type
-- Show new numbers and heat maps
-- Re-do logistic models, extrapolate but divided by hosts

Note that ability to examine different facets of the data is coming to an interactive website soon.
